\documentclass[10pt]{exam}
\usepackage[hon]{template-for-exam}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage{multicol}
\usetikzlibrary{shadings,decorations.pathmorphing,arrows.meta}



\def\mytitle{Chapter 3 (Two-Dimensional Kinematics)}
\author{Rohrbach}
\date{\today}

\def\mymaketitle{
  \begin{flushleft}
    {\LARGE \textbf \mytitle \par}
  \end{flushleft}
}


\newcommand{\bs}[2]{\textbf{#1} (\sc #2 Points)}


\begin{document}


\mymaketitle



\newcommand{\stampbox}[1]{

  \hfill
  \begin{tikzpicture}[every text node part/.style={align=center}]
     \node[gray!50,draw,rounded corners] at (0,0) 
      {\sc Stamp \\ \sc Here \\ \small #1 \sc Points};
  \end{tikzpicture}
  \vspace{1em}
  
  \hrule

}

\section*{Homework Check A (collected \fillin[][6em])}


%%%%%%%%%%%

\subsection*{Reading}

Please read the following on your own in the OpenStax textbook by the dates given.  It will give good context for class discussion.  Check off when you have completed them.

\vspace{1em}

\begin{checkboxes}
  \choice 3.1 Kinematics in 2D: An Intro \dotfill \fillin[][6em]
  \choice 3.2 Vector Addition \& Subtraction: Graphical Methods \dotfill \fillin[][6em]
  \choice 3.3 Vector Addition \& Subtraction: Analytical Methods \dotfill \fillin[][6em]
  \choice 3.4 Projectile Motion \dotfill \fillin[][6em]
\end{checkboxes}


\subsection*{Problems and Conceptual Question}


Get stamps from your instructor as you complete each of the following problems.  The conceptual questions (CQ) require at least one sentence of explanation.

\vspace{1em}

\noindent
{\sc Stamps will not be given if work is not shown on a separate sheet of paper}

\vspace{1em}


\begin{tabular}{|*{2}{p{7cm}|}}
  \hline
  %
  \bs{3.2 Graphical Methods}{5}  & \bs{3.3 Analytical Methods}{10}  \\
  P \#1,2,4                      &  P \#13,15,16,18,20-23           \\
  CQ \#1,3,4,5,7                 &  CQ \#9-11                       \\
                                 & \textbf{HW Quiz on \fillin[][6em]}\\[2.5cm]\hline
  %
  \bs{3.4 Projectiles (Part I)}{5}  \\
  P \#25,27,40                      \\
                                    \\[2.5cm]\cline{1-1}
  %

\end{tabular}


  

%%%%%%%%%%%%%

\subsection*{Problem Answers}

\begin{multicols}{3}

  \begin{itemize}[noitemsep]
    \item[1. ] (a) 480 m \\ 
               (b) $\approx 380$ m @ $20^\circ$ E of N
    \item[2. ] (a) 1.20~km \\
               (b) $\approx 380$ m @ $70^\circ$ N of E 
    \item[4. ] $\approx 31$ m @ $35^\circ$ W of N
    \item[13.] (a) 1.56 km; (b) 120 m east
    \item[15.] $S_x=S_y=\SI{87.0}{km}$
    \item[16.] 30.8 m @ 35.8$^\circ$ W of N
    \item[18.] $R_x = 1.94$~km; $R_y = 7.24$~km
    \item[20.] 92.3 m @ 53.7$^\circ$ S of W
    \item[21.] 18.4 km south, then 26.2 km west
    \item[22.] 2.97 km @ 22.2$^\circ$ W of S
    \item[23.] 7.34 km @ 63.5$^\circ$ S of E
    \item[25.] $x=\SI{1.30e2}{m}$; $y=\SI{30.9}{m}$
    \item[27.] (a) 3.50 s \\
               (b) 28.6 m/s \\
               (c) 34.3 m/s \\
               (d) 44.7 m/s @ 50.2$^\circ$ below horiz
  \item[40.] 10.3~m/s @ 73.1$^\circ$ below horiz
    
  \end{itemize}
  
\end{multicols}



%%%%%%%%%%%%%
%%%%%%%%%%%%%

\pagebreak

\mymaketitle

\section*{Homework Check B (collected on Test Day - \fillin[][6em])}

\subsection*{Reading}

Please read the following on your own in the OpenStax textbook by the dates given.  It will give good context for class discussion.  Check off when you have completed them.

\vspace{1em}

\begin{checkboxes}
  \choice 3.5 Addition of Velocities \dotfill \fillin[][6em]
\end{checkboxes}


\subsection*{Problems and Conceptual Question}


Get stamps from your instructor as you complete each of the following problems.  The conceptual questions (CQ) require at least one sentence of explanation.

\vspace{1em}


\begin{tabular}{|*{2}{p{7cm}|}}
  \hline
  %
  \bs{3.4 Projectiles (Part II)}{10}  & \bs{3.5 Addition of Velocities}{5}  \\
  P \#29,35,41,43,45                  & P \#53,54,57 \\
  CQ \#13-15                          & CQ \#17-20      \\[2.5cm]\hline

\end{tabular}



\subsection*{Problem Answers}

\begin{multicols}{3}

  \begin{itemize}[noitemsep]
    \item[29.] (a) 18.4$^\circ$ \\
               (b) over the branch
    \item[35.] 1.50 m (launch angle of 45$^\circ$)
    \item[41.] 4.23 m; misses the nest
    \item[43.] No. Max range $\approx 92$ m
    \item[45.] 15.0 m/s
    \item[53.] (a) 5.00~m/s; -4.00~m/s \\
               (b) 13.00 m/s; 7 min 42 sec
    \item[54.] (a) 0.70 m/s faster \\
               (b) second runner wins \\
               (c) 4.17 m
    \item[57.] 8.05~m/s @ 81.8$^\circ$ N of E
  \end{itemize}
  
\end{multicols}


\subsection*{Bonus Problems}
\begin{tabular}{|*{4}{p{3.5cm}|}}
  \hline
  %
  P \#37  &  P \#47  &  P \#61  &  P \#67 \\[2.5cm]
  %
  \hline
\end{tabular}

\vspace{1em}
\hrule
\vspace{1em}

\noindent
{\footnotesize Homework will be accepted for full credit until the test.  Homework turned in after the test will be accepted for half credit until the Unit 4 Test.
\emph{Please remember that you will not be eligible to complete test corrections if you do not turn in your homework.}}



\end{document}