\documentclass[10pt]{exam}
\usepackage[hon]{template-for-exam}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage{multicol}



\def\mytitle{Chapter 2 (One-Dimensional Kinematics)}
\author{Rohrbach}
\date{\today}

\def\mymaketitle{
  \begin{flushleft}
    {\LARGE \textbf \mytitle \par}
  \end{flushleft}
}

\newcommand{\printeqs}{
  \section*{Equations} 
  
  \begin{center}
    \begin{tabular}{cccccc}
      $\bar{v} = \frac{\Delta x}{\Delta t}$       &   
      $\bar{a} = \frac{\Delta v}{\Delta t}$       &&
      $v = v_0 + a t$                             &
      $x = x_0 + v_0t + \frac{1}{2}at^2$          &
      $v^2 = v_0^2 + 2a \left( x - x_0 \right) $  \\
          & & & ``Old Faithful'' & ``Big Chalupa'' & ``Ain't Got No Time'' \\
    \end{tabular}
  \end{center}
}

\begin{document}


\mymaketitle



\newcommand{\stampbox}[1]{

  \hfill
  \begin{tikzpicture}[every text node part/.style={align=center}]
     \node[gray!50,draw,rounded corners] at (0,0) 
      {\sc Stamp \\ \sc Here \\ \small #1 \sc Points};
  \end{tikzpicture}
  \vspace{1em}
  
  \hrule

}

\section*{Homework Check A (collected Mon Aug, 15)}


%%%%%%%%%%%


\paragraph{Velocity and Speed} p. 43 \#1, 2, 4 
\dotfill Complete by Thu, Aug 11

\stampbox{3}


%%%%%%%%%%%

\paragraph{Average Velocity} p. 43 \#7, 9, 12
\dotfill Complete by Thu, Aug 11

\stampbox{5}

%%%%%%%%%%%%

\paragraph{Acceleration} pp. 43-44 \#17, 18, 19, 20
\dotfill Complete by Thu, Aug 11

\stampbox{5}
  

%%%%%%%%%%%%

\paragraph{Graphical Analysis} p. 45 \#55, 57, 58
\dotfill Complete by Mon, Aug 15

{\sc There is not much work to show for these problems; 
you can provide just answers.}

\stampbox{2}


%%%%%%%%%%%%%

\subsection*{Answers}

\begin{multicols}{3}

  \begin{itemize}[noitemsep]
    \item[1.]  52.7 m
    \item[2.]  85.5 km/h
    \item[4.]  $-4.06$ cm/s
    \item[7.]  distance is 350 km; \\
               avg velocity is 77.7 km/h
    \item[9.]  avg vel is zero; \\
               avg speed is 3.68 m/s
    \item[12.] avg vel is zero; \\
               avg speed is 61.1 km/h
    \item[17.] 6.1 m/s/s
    \item[18.] 6.52 m/s/s = 84,500 km/h/h
    \item[19.] $-6$ m/s/s = $-0.61$ g
    \item[20.] 8.5 seconds
    \item[55.] a) t=48 sec;  \\ 
               b) $\SI{90}{\second} < t < \SI{105}{\second}$; \\
               c) $\SI{0}{\second} < t < \SI{40}{\second}$; \\
               d) $t=\SI{70}{\second}$
    \item[57.] a) about 0.3 m/s;  \\
               b) about 1.3 m/s;  \\
               c) about 0.4 m/s;  \\
               d) about 1.6 m/s;  \\ 
               e) about $-1$ m/s
    \item[58.] a) $\SI{0}{\second} < t < \SI{15}{\second}$;;  \\
               b) either around $t=29$ s or $t=45$ s; \\
               c) about $t=37$ s; \\
               d) moves forward for 37 sec \\ \hspace*{5em} then backwards
  \end{itemize}
  
\end{multicols}

\noindent
{\footnotesize Homework will be accepted for full credit until the test.
Homework turned in after the test will be accepted for half credit
until the Unit 3 Test.
\emph{Please remember that you will not be eligible to complete 
test corrections if you do not turn in your homework.}}

\vspace{1em}
\hrule 
\printeqs


%%%%%%%%%%%%%
%%%%%%%%%%%%%

\pagebreak

\mymaketitle

\section*{Homework Check B (collected on Test Day)}

\paragraph{Motion at a Constant Acceleation} pp. 44 \#22, 23, 24, 29
\dotfill Complete by Thu, Aug 18.
   
{\sc Your work for these problems should include pictures!}
\hfill \textbf{\emph{Homework Quiz}}

\stampbox{5}

%%%%%%%%%%%%%%

\paragraph{Falling Objects} pp. 44-45 \#39, 40, 41, 49, 52
\dotfill Complete by Fri, Aug 19.
   
{\sc Your work for these problems should include pictures!}

\stampbox{5}

%%%%%%%%%%%%%%

\paragraph{Conceptual Questions} p. 41 \#1, 2, 3, 4, 6, 9, 10, 16, 17
\dotfill Complete by Mon, Aug 22.
   
{\sc These questions should have at least one full sentence 
      of explanation}

\stampbox{5}

%%%%%%%%%%%%%%

\paragraph{Misconceptual Questions} p. 42 \#2, 3, 4, 5, 6, 9
\dotfill Complete by Mon, Aug 22.
   
{\sc You do not need to get this one stamped,
but these are good review for your test!}

\vspace{1em}
\hrule

%%%%%%%%%%%%%%

\paragraph{Bonus Problems!} p. 43 \#15; p. 44 \#32 \& 38; p. 45 \#53
\dotfill Turn in separately on test day!
  

\vspace{1em}
\hrule

%%%%%%%%%%%%%%

\paragraph{Test will be on Tuesday, Aug 23.} \hfill


\subsection*{Problem Answers}

\begin{multicols}{3}

  \begin{itemize}[noitemsep]
    \item[22.] $-4.5$ m/s/s
    \item[23.] 1.17 m/s/s; 105 m
    \item[24.] 204 m
    \item[29.] $-435$ m/s/s = $-44.4 g$'s
    \item[39.] 61.8 m
    \item[40.] 8.8 s;  86.3 m/s
    \item[41.] 16.7 m/s;  14.2 m
    \item[49.] 5.21 s
    \item[52.] 23.4 m/s; \\ 
               28 m above the ground; \\
               0.96 s before seen at window; \\
               4.78 s after being thrown
    
  \end{itemize}
  
\end{multicols}

\subsection*{Misconceptual Answers}

\begin{multicols}{9}

  \begin{itemize}[noitemsep]
    \item[2.] d 
    \item[3.] d 
    \item[4.] c 
    \item[5.] a
    \item[6.] c
    \item[9.] a
    
  \end{itemize}
  
\end{multicols}
  
\noindent
{\footnotesize Homework will be accepted for full credit until the test.
Homework turned in after the test will be accepted for half credit
until the Unit 3 Test.
\emph{Please remember that you will not be eligible to complete 
test corrections if you do not turn in your homework.}}

\vspace{1em}
\hrule 
\printeqs


\end{document}