\documentclass[10pt]{exam}
\usepackage[hon]{template-for-exam}
\usepackage{tikz,ifthen}
\footer{\emph{\small Example Problems: Ch 2 (One-Dimensional Motion)}}{}{\sc \myclass}


\title{Chapter 2 Example Problems}
\author{Rohrbach}
\date{\today}

\begin{document}
\maketitle

\def\mystrut{\protect\rule[-2.2ex]{0ex}{2.2ex}} 
\qformat{ \textbf{Example Problem 3-\thequestion}
  \ifthenelse{\equal{\thequestion}{\thequestiontitle}}
    {}
    {: \emph{\thequestiontitle}}
  \mystrut  \hfill}
\begin{questions}
  
\titledquestion{Kinematic Equations}
  A minivan starts at rest and then accelerates at a rate of 3 m/s$^2$ for 10 seconds.  How far does the minivan travel in this time?
  \vs 

\question
  In coming to a stop, a car leaves skid marks 65 meters long on the highway.  Assuming a deceleration of 4.0~m/s$^2$, estimate the speed of the car just before braking. 
  \vs 

\question
  You are traveling at 24 m/s on the onramp.  As you get ready to merge onto the interstate, you accelerate over a distance of 50 meters to 46 m/s.  What was your acceleration?
  \vs 

\pagebreak

\titledquestion{Free Fall}
  The Eiffel Tower is 324 meters tall.  If we make the (totally unrealistic) assumption that there is no air resistance, how fast would a penny dropped from the Eiffel Tower be travelling when it hit the ground?
  \vs 


\titledquestion{Throwing Cats}
  You have a kitten named Mittens.  You toss Mittens into the air at an initial velocity of 8~m/s. 
  
  \begin{parts}
    \part
      How high will Mittens go before coming back down (at which point you will---of course---gently catch her)?
    \part
      What is the total time that Mittens is in the air?
    \part
      What is her velocity just before you catch her?

  \end{parts}
  \vs
  



\end{questions}




\end{document}