\documentclass[10pt]{exam}
\usepackage[hon]{template-for-exam}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage{multicol}



\def\mytitle{Chapter 2 (One-Dimensional Kinematics)}
\author{Rohrbach}
\date{\today}

\def\mymaketitle{
  \begin{flushleft}
    {\LARGE \textbf \mytitle \par}
  \end{flushleft}
}

\newcommand{\printeqs}{
  \section*{Equations} 
  
  \begin{center}
    \begin{tabular}{cccccc}
      $\bar{v} = \frac{\Delta x}{\Delta t}$       &   
      $\bar{a} = \frac{\Delta v}{\Delta t}$       &&
      $v = v_0 + a t$                             &
      $x = x_0 + v_0t + \frac{1}{2}at^2$          &
      $v^2 = v_0^2 + 2a \left( x - x_0 \right) $  \\
          & & & ``Old Faithful'' & ``Big Chalupa'' & ``Ain't Got No Time'' \\
    \end{tabular}

    \vspace{1em}

    $\SI{1}{\meter\per\second}=\SI{3.6}{\kilo\meter\per\hour}$
  \end{center}
}

\newcommand{\bs}[2]{\textbf{#1} (\sc #2 Points)}

\begin{document}


\mymaketitle



\newcommand{\stampbox}[1]{

  \hfill
  \begin{tikzpicture}[every text node part/.style={align=center}]
     \node[gray!50,draw,rounded corners] at (0,0) 
      {\sc Stamp \\ \sc Here \\ \small #1 \sc Points};
  \end{tikzpicture}
  \vspace{1em}
  
  \hrule

}

\section*{Homework Check A (collected Fri, Aug 15)}

%%%%%%%%%%%

\subsection*{Reading}

Please read the following on your own in the OpenStax textbook by the dates given.  It will give good context for class discussion.  Check off when you have completed them.

\vspace{1em}

\begin{checkboxes}
  \choice 2.1 Displacement \dotfill Wed, Jul 30
  \choice 2.2 Vectors, Scalars, and Coordinate Systems \dotfill Thu, Jul 31
  \choice 2.3 Time, Velocity, and Speed \dotfill Fri, Aug 1
  \choice 2.4 Acceleration \dotfill Tue, Aug 5 
  \choice 2.8 Graphical Analysis \dotfill Fri, Aug 8
\end{checkboxes}


\subsection*{Problems and Conceptual Question}


Get stamps from your instructor as you complete each of the following problems.  The conceptual questions (CQ) require at least one sentence of explanation.

\vspace{1em}


\begin{tabular}{|*{2}{p{7cm}|}}
  \hline
  %
  \bs{2.1}{3}    & \bs{2.3}{3}  \\
  P \#1-4        &  P \#5,7     \\
  CQ \#2-3       &  CQ \#6      \\[2.5cm]\hline
  %
  \bs{2.4}{5}   & \bs{2.8}{4}  \\
  P \#16,17,19  &  P \#59,61   \\
  CQ \#13-15    &  CQ \#26-28  \\[2.5cm]\hline
  %

\end{tabular}



\vspace{1em}
\hrule 
\printeqs


%%%%%%%%%%%%%
%%%%%%%%%%%%%


\pagebreak

\mymaketitle

\section*{Homework Check B (collected on Test Day - Tue, Aug 26)}

\subsection*{Reading}

Please read the following on your own in the OpenStax textbook by the dates given.  It will give good context for class discussion.  Check off when you have completed them.

\vspace{1em}

\begin{checkboxes}
  \choice 2.5 Motion Equations \dotfill Wed-Thu, Aug 11-12
  \choice 2.6 Problem Solving Basics \dotfill Wed-Thu, Aug 11-12
  \choice 2.7 Falling Objects \dotfill Mon, Aug 18
\end{checkboxes}


\subsection*{Problems and Conceptual Question}


Get stamps from your instructor as you complete each of the following problems.  The conceptual questions (CQ) require at least one sentence of explanation.

\vspace{1em}


\begin{tabular}{|*{2}{p{7cm}|}}
  \hline
  %
  \bs{2.5}{10}                & \bs{2.7}{10}  \\
  P \#20,22,23,27,28,30,31    & P \#41,43,45,47,49,51 \\
  \textbf{HW Quiz on Mon, Aug 18} & CQ \#20,21,22,24      \\[2.5cm]\hline

\end{tabular}



%%%%%%%%%%%%%%

\vspace{1em}

\hrule

\paragraph{Bonus Problems!} P\#32, 55, 57
\dotfill Turn in separately on test day!
  

\vspace{1em}
\hrule

%%%%%%%%%%%%%%

\paragraph{Test will be on Tue, Aug 26.} \hfill




\vspace{1em}
\hrule 
\printeqs


\end{document}