 
 \documentclass[12pt]{exam}
\usepackage[hon]{template-for-exam}
\usepackage{tikz,ifthen,multicol,silence}
\footer{}{}{}
\header{}{}{}
\shadedsolutions
%\printanswers
\usetikzlibrary{shadings,decorations.pathmorphing,arrows.meta,patterns}
\WarningFilter{latex}{Label `question}
\WarningFilter{latex}{There were multiply-defined labels}


\newcommand{\prob}{

  \noindent
  Sara, an amazingly well-rounded athlete, participates in a grueling race. Use the information to determine the answers to each question.

 \begin{questions}
 
  \question 
      Sara begins the race by running 5~km from the starting line to checkpoint~A in 20 minutues and 40 seconds.  What is her velocity (in m/s)?
    \question
      Next, Sara swims \SI{500}{\meter} from checkpoint~A to checkpoint~B with a velocity of \SI{1.1}{\meter\per\second}.  How much time does it take her?
    \question
      From checkpoint~B she rides a bike with a velocity of 4.9 m/s for 1~hour.  What is the distance between checkpoint~B to checkpoint~C?
    \question
      Sara must now run all the way back to the starting line to finish the race.  Completely exhausted, Sara climbs into her single-engine airplane and flies back to the starting line.  What is her velocity to go from checkpoint~C to the starting line if the plane ride is 19 minutes and 17 seconds?
    \question
      Calculate Sara's {\bf average speed} for the entire race and her {\bf average velocity}.
 \end{questions}
}


\begin{document}

  \large

  \prob
  \hrule
  \vs
  \prob

\end{document}
