\documentclass[10pt]{exam}
\usepackage[phy]{template-for-exam}

\title{Vectors Practice}
\author{Rohrbach}
\date{\today}

\begin{document}
\maketitle

\begin{questions}

\uplevel{For each problem, start by {\bf drawing the triangle}.  Then complete the calculations.}

\question
  Sandy Squirrel travels 18 m east and 41 m north to get to her secret stash of Emerald Nuts.  Chester Chipmunk decides to take a short cut and travel in a straight line to the location of the (not so) secret stash.  How far did he travel and at what angle?
  \vs

\question
  An airplane is taking off at a 57° angle with a velocity of 45 m/s.  How fast is it traveling across the ground, as well as into the air?
  \vs

\question
  An airplane is flying at 80 km/hr N, and experiences a crosswind of 20 km/hr E.  What is magnitude and direction of the resultant velocity of the plane?
  \vs


\pagebreak

\question
  A javelin is flying toward the ground at a speed of 30 m/s at an angle of 55 degrees below the horizon.  Find the $x$- and $y$- components of the javelin's velocity.
  \vs

\begin{EnvUplevel}
  \paragraph{Review.} 
    Try some of these problems to remind yourself how to use the kinematic equations.


    \begin{center}
      \begin{tabular}{*{3}{p{10em}}c}
        \\
        \centering $v_f=v_i+at$ &
        \centering $d=v_i t + \tfrac{1}{2} at^2$ &
        \centering $v_f^2 = v_i^2 + 2ad$ & \\
        \centering \it\small ``Old Faithful'' &
        \centering \it\small ``The Big Chalupa'' &
        \centering \it\small ``Ain't Got no Time'' & \\
        \\
      \end{tabular}
    \end{center}
\end{EnvUplevel}

\question  
  You drop a puppy off the side of a cliff.  How much time does it take to fall 3.8 meters?
  \vs

\question  
  You drop kick a soccer ball straight up in the air with a velocity of 13.1 m/s.  
  
  \begin{parts}
    \part 
      What maximum height does the soccer ball reach?
      \vs

    \part 
      How much time is the soccer ball in the air?
      \vs
  \end{parts}


\end{questions}

\end{document}