\documentclass[10pt]{exam}
\usepackage[phy]{template-for-exam}
\usepackage{cclicenses,hyperref}

\title{Projectiles \#3}
\author{Rohrbach}
\date{\today}

\begin{document}
\maketitle

\begin{questions}
  

\question
Evel Knievel is attempting to jump his motorcycle from the roof of one building to the roof of another building that has the same height.  To do so he rides at 25 m/s and uses a ramp with a $33^\circ$ angle.

\begin{parts}
  \part
    Draw a diagram of the situation and write down knowns and unknowns.
    \vs
  
  \part
    What are the $x$- and $y$- components of Evel's initial velocity?
    \vs
  
  \part
    How much time will it take Evel to land?
    \vs
  
  \part
    How far forward will he travel in this time?
    \vs
  
  \part
    The buildings are 50 meters apart.  Did he make it?
    \vspace{3em}

\end{parts} 

\pagebreak

\question
A ball is thrown \emph{horizontally} from the top of a 60-m building and lands 100~m from the base of the building.


\begin{parts}
  \part
    Draw a diagram of the situation and write down knowns and unknowns.
    \vs
  
  \part
    How long is the ball in the air?
    \vs
  
  \part
    What must have been the initial horizontal component of the velocity?
    \vs
  
  \part
    Calculate the final $x$- and $y$- velocities of the ball just before it hist the ground.
    \vs
  
  \part
    What is the final resultant velocity and angle of the ball just before it hist the ground?
    \vs

\end{parts} 

    \uplevel{
      \footnotesize Answers: 
      (b) 3.50 s; 
      (c) 28.6 m/s; 
      (d) 34.3 m/s; 
      (e) 44.7 m/s @ $-50.2^\circ$

    
      \vspace{1em}

      Problem Credit: OpenStax \emph{College Physics 2e}. Authored by: P.P Urone, R. Hinrichs, et al.


      License: \cc\hspace{-1em}\ccby  CC BY: Attribution.

      Retrieved 2025-10-27 from \texttt{\href{https://openstax.org/books/college-physics-2e/pages/3-problems-exercises}{https://openstax.org/books/college-physics-2e/pages/3-problems-exercises}}
    }

\end{questions}
\end{document}