\documentclass[10pt]{exam}
\usepackage[hon]{template-for-exam}
\usepackage{multirow,multicol}
\usepackage[table,dvipsnames]{xcolor}
\usepackage{pgf-pie}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{graphicx}
\graphicspath{{./images}}
\setlist[enumerate,itemize]{topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex}
\usepackage[super]{nth}


\newcommand{\mg}{\rowcolor{Goldenrod}}


\title{Honors Physics Spring Semester}
\author{Rohrbach}


\begin{document}

\maketitle

\noindent Zachary J. Rohrbach, Instructor

\noindent (317) 544-5000 x5131

\noindent \texttt{ZJRohrbach@avon-schools.org}

\section*{Units Covered}

\begin{multicols}{2}
  \begin{description}
    \item [Ch 7] Momentum
    \item [Ch 8] Rotation
    \item [Ch 11A] Simple Harmonic Motion 
    \item [Ch 11B] Waves
    \item [Ch 16-19] Electricity
    \item [Ch 20-21] Magentism
    \item [Ch 23] Optics (\emph{time permitting})
    \item [] \hfill
  \end{description}
\end{multicols}

\section*{Tests and Quizzes}

Chapters 7 and 8 will continue as last semester, with open-note HW quizzes, tests, and test corrections.  

Starting with Chapter 11A, the course will consist of shorter units, and the methods of evaluation will change accordingly: There may be a few HW quizzes, but they will not necessarily occur every unit.  Also tests will be shorter.  Because of this, \emph{test corrections will not be offered for Ch 11A onward.}



\section*{Methods of Evaluation}

Your pre-exam grade will be based on the methods of 
evaluation shown below. The weighting of each of these 
categories is subject to change. Your overall class 
grade will consist of the pre-exam grade (85\%) and the
final exam grade (15\%).

\begin{enumerate}
	\item	Homework (30\%)
	\begin{itemize}
		\item 
			Homework plays an important role in helping you understand the material.  Therefore, it is important that it gets done in a timely manner! 
		\item 
			Homework is accepted for full credit until Test Day.  There will be a 50\% penalty for homework turned in after test day.  Homework will not be accepted any later than the Test for the following unit.
    \item 
      There is guaranteed to be open-note HW Quizzes for Ch 7 and 8.  
	\end{itemize}
	\item	Labs/Projects (30\%)
	\begin{itemize}
		\item 
			Late labs will be assessed a penalty of 10\% per school day (whether or not class meets) up to 50\%.  Labs that are more than a month late will not be accepted.
		\item 
		  {\bf There is a research project in the Spring Semester.  If you complete your research project late, it is immediately assessed a 50\% penalty.}
	\end{itemize}
	\item	Tests (40\%)
	\begin{itemize}
		\item	
			Each chapter will end with a quiz or a test.
		\item 
			Tests corrections will be available for Chapter 7 and Chapter 8 Tests.  Similar to last semeseter, you will only be eligible for test corrections if you've done your homework.
    \item 
      All tests given after Chapter 8 will be shorter ``mini-tests,'' which will not be elibgible for test corrections.
	\end{itemize}
	
\end{enumerate}






\end{document}