\documentclass[10pt]{exam}
\usepackage[phy]{template-for-exam}

\title{Unit 09 Review Problems (Sound \& Light)}
\author{Rohrbach}
\date{\today}

\begin{document}
\maketitle

\newcommand{\printeq}{
  \hrule
  \small
  \begin{align*}
      v   &=  f\lambda
    & f   &= f_s \left( \frac{v\pm v_o}{v\mp v_s} \right)
    & \frac{1}{d_i} + \frac{1}{d_o} &= \frac{1}{f}
    & M &= \frac{h_i}{h_0} = \frac{-d_i}{d_o}
  \end{align*}
  %
  \begin{align*}
    \text{Speeds of Sound: } & 
    & \text{air: }   & \SI{340}{\meter\per\second}
    & \text{water: } & \SI{1530}{\meter\per\second}
    & \text{iron: }  & \SI{5100}{\meter\per\second}
  \end{align*}
  \hrule
}

\printeq

\begin{questions}

\question
  You are driving {\bf north} at 17~m/s when you see a police car in your rearview mirror that is also driving {\bf north}, but at 32~m/s. 

  \begin{parts}
    \part 
      If the police car produces a frequency of 6000 Hz, what frequency do you hear? \vs 

    \part
      You pull over to the side of the road and come to a stop as the police car approaches, what sound do you hear now? \vs 

    \part
      You are still at rest at the side of the road, but the cruiser now passes you.  What sound do you now hear? \vs 

  \end{parts}

\question
  Red light has a wavelength of \SI{5.90e-7}{\meter}.  What is the frequency of red light? \vs 

\question
  Find the wavelength of a \SI{10000}{\hertz} sound when it travels through the air. \vs

\fullwidth{
  \footnotesize
  Answers: 
  \hfill 1. (a) \SI{6955}{\hertz}
  \hfill (b) \SI{6623}{\hertz}
  \hfill (c) \SI{5484}{\hertz}
  \hfill
  \hfill 2. \SI{5.08e14}{\hertz}
  \hfill 3. \SI{0.034}{\meter}

}

\pagebreak

\uplevel{\printeq}

\question
Consider a converging lens with a focal length of 2 cm. An object is 10 cm away.

\begin{parts}
    \part What is the distance between the lens and the image? \vs
    \part What is the magnification of the image? \vs
    \part Is the image real or virtual? How do you know? \vs
\end{parts}

\question
Consider a \emph{diverging} lens with a focal length of 3~cm. An object is 4~cm away.

\begin{parts}
    \part What is the distance between the lens and the image? \vs
    \part What is the magnification of the image? \vs
    \part Is the image real or virtual? How do you know? \vs
\end{parts}


\end{questions}

\fullwidth{
  \footnotesize
  Answers: 
  \hfill 4. (a) \SI{2.5}{\centi\meter}
  \hfill (b) \SI{-0.4}{}
  \hfill (c) real
  \hfill
  \hfill 5. (a) \SI{-6.0}{\centi\meter}
  \hfill (b) \SI{1.5}{}
  \hfill (c) virtual 
}



\end{document}