\documentclass[10pt]{exam}
\usepackage[phy]{template-for-exam}

\title{Unit 04 Review (Forces \& Newton's Laws)}
\author{Rohrbach}
\date{\today}


\newcommand{\printeqs}{
  \begin{center}
    \begin{tabular}{|*9c|}
      \hline 
      &&&&&&&&\\
      &
      $F_{NET}=ma$ &&
      $F_{NET}=\pm F_1 \pm F_2 \pm \cdots$ &&
      $F_G=mg$ &&
      $g=\SI{9.8}{\meter\per\second^2}$ &
      \\
      \hline
    \end{tabular}
  \end{center}
}

\begin{document}
\maketitle

\printeqs

\begin{questions}

\question
  A penguin by the name of Pickles ($m=23$ kg) is standing on a scale in an elevator on the top floor of a building.  The elevator begins to go down towards the ground floor and does so by accelerating downward at 2.7 m/s$^2$.  What is the normal force?
  \vs

\question
  A new sports car ($m=980$ kg) is capable of applying a force of 5500 N with its engine.  If the force of friction on the car is 500 N, what is the car's acceleration (assume no air resistance)? 
  \vs

\question
  You are pushing a large tub of chocolate, which has a mass of 455 kg, with an acceleration of 0.4 m/s$^2$.  The force of friction is 88 N.  What is the force with which you are pushing the tub?
  \vs

\question
  A fish ($m=9.1$ kg) is pulled straight up out of the water by a fisherman.  What is the acceleration of the fish if the force applied by the fisherman is 120 N?
  \vs

\noindent {\footnotesize Answers: (1) 163.3 N; (2) 5.10 m/s$^2$; (3) 270 N; (4) 3.39 m/s$^2$}

\pagebreak

\question
  Definitions:
  
  \begin{parts}
    \part mechanical equilibrium \vspace{2em}
    \part inertia \vspace{2em}
    \part weight \vspace{2em}
    \part mass \vspace{2em}
    \part $F_G$ \vspace{2em}
    \part $g$ \vspace{2em}
  \end{parts}



\question
  List each of Newton's Laws \vs

\question
  If Newton's third law is correct, then a tiny smart car feels the same force as a huge semi-truck when the two have a head on collision.  Why would you rather be riding in the semi-truck? \vs

\question
  Explain which of Newton's 3 laws best describes the situation.
  \begin{parts}
    \part You are drinking a cup of coffee while driving.  When you slam on the brakes, your coffee spills out. \vs
    \part If you are standing in a boat, and step out onto the dock, the boat moves away from you. \vs
    \part As you add more items to a grocery cart, you notice its acceleration decreases. \vs
    \part You are wearing roller blades and stand facing a brick wall.  You push forward, against the wall, but end up traveling backwards.  Why? \vs
  
  \end{parts}
  

\end{questions}

\end{document}