\documentclass[10pt]{exam}
\usepackage[hon]{template-for-exam}

\title{Orbital Motion PhET Simulation}
\author{Rohrbach}
\date{\today}

\begin{document}
\maketitle

\noindent
On Schoology, find the link to the “Gravity and Orbits” PhET Simulation

\begin{questions}
  \question
    Start by looking at the {\bf earth-moon system}. Turn on all four checkboxes on the right hand side

  \begin{parts}
    \part 
      Is there anything unexpected about the motion of the moon and/or the earth?
      \vs

    \part
      On the right side of the screen, find the button that turns gravity off.  What happens when you turn gravity off?  Why does this make sense?
      \vs 

    \part
      Change the velocity of the moon by dragging on the ``$v$'' circle.  Decrease the velocity.  Explain what happens and why that makes sense.
      \vs 

  \end{parts}



  \question
    Switch to the {\bf earth-sun system}.  Adjust the velocity until you can get an elliptical path. What do you notice about the velocity of the earth as it orbits the sun (when does it speed up, when does it slow down, or is it constant through its entire motion)?
    \vs



  \question
    Click ``stop'' and switch to a {\bf sun-earth-moon} system.

    \begin{parts}
      \part
        Which object (or objects) is the Moon orbiting (hint: this is kind of a trick question)?
        \vs 

      \part
        Turn the ``traces'' checkmark on.  Explain why the moon's path is different on the right side of the sun, than on the left.
        \vs

    \end{parts}



\end{questions}



\end{document}