\documentclass[10pt]{exam}
\usepackage[hon]{template-for-exam}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage{multicol}
\usetikzlibrary{shadings,decorations.pathmorphing,arrows.meta}



\def\mytitle{Chapters 4-5 (Dynamics, Forces, Newton's Laws)}
\author{Rohrbach}
\date{\today}

\def\mymaketitle{
  \begin{flushleft}
    {\LARGE \textbf \mytitle \par}
  \end{flushleft}
}


\newcommand{\bs}[2]{\textbf{#1} (\sc #2 Points)}


\begin{document}


\mymaketitle



\newcommand{\stampbox}[1]{

  \hfill
  \begin{tikzpicture}[every text node part/.style={align=center}]
     \node[gray!50,draw,rounded corners] at (0,0) 
      {\sc Stamp \\ \sc Here \\ \small #1 \sc Points};
  \end{tikzpicture}
  \vspace{1em}
  
  \hrule

}

\section*{Homework Check A (collected by Fall Break - Oct 10)}


%%%%%%%%%%%

\subsection*{Reading}

Please read the following on your own in the OpenStax textbook by the dates given.  It will give good context for class discussion.  Check off when you have completed them.

\vspace{1em}

\begin{checkboxes}
  \choice 4.1 Development of the Force Concept \dotfill Fri, Sept 26
  \choice 4.2 Newton's First Law: Inertia \dotfill Mon, Sept 29
  \choice 4.3 Newton's Second Law: Concept of a System \dotfill Tue, Sept 30
  \choice 4.4 Newton's Third Law: Symmetry in Forces \dotfill Tue, Sept 30
  \choice 4.5 Normal, Tension, and Other Forces \dotfill Fri, Oct 3
\end{checkboxes}


\subsection*{Problems and Conceptual Question}


Get stamps from your instructor as you complete each of the following problems.  The conceptual questions (CQ) require at least one sentence of explanation.

\vspace{1em}

\noindent
{\sc Stamps will not be given if work is not shown on a separate sheet of paper}

\vspace{1em}


\begin{tabular}{|*{2}{p{7cm}|}}
  \hline
  %
  \bs{Forces \& Newton's Laws}{5} 
                   & \bs{Single Body}{5}  \\
  P \#1-2                 & P \#4-7       \\
  CQ \#2-6,8,10,15,18,A,B &  CQ \#23      \\
                          &               \\[2.5cm]\hline
  %
  \bs{Multi Body}{5}                 \\
  P \#9-14                          \\
  \textbf{HW Quiz on Tue, Oct 7}.\\[2.5cm]\cline{1-1}
  %

\end{tabular}


\section*{Equations}

\begin{align*}
  \Sigma \vec{F} &= m\vec{a} &
  w &= mg 
\end{align*}



%%%%%%%%%%%%%
%%%%%%%%%%%%%

\pagebreak

\mymaketitle

\section*{Homework Check B (collected on Test Day - Tue, Nov 4)}

\subsection*{Reading}

Please read the following on your own in the OpenStax textbook by the dates given.  It will give good context for class discussion.  Check off when you have completed them.

\vspace{1em}

\begin{checkboxes}
  \choice 5.1 Friction \dotfill Tue, Oct 28
\end{checkboxes}


\subsection*{Problems and Conceptual Question}


Get stamps from your instructor as you complete each of the following problems.  The conceptual questions (CQ) require at least one sentence of explanation.

\vspace{1em}


\begin{tabular}{|*{2}{p{7cm}|}}
  \hline
  %
  \bs{Friction}{5}       & \bs{Forces at an Angle}{5}  \\
  P \#14-16              & P \#17-18     \\
                         & CQ C-D        \\[2.5cm]\hline

\end{tabular}



\subsection*{Bonus Problems}

\hfill

\begin{tabular}{|*{4}{p{3.3cm}|}}
  \hline
  %
  P \#4  &  P \#9  &  P \#20  &  P \#21 \\[2.5cm]
  %
  \hline
\end{tabular}

\vspace{1em}
\hrule
\vspace{1em}

\noindent
{\footnotesize Homework will be accepted for full credit until the test.  Homework turned in after the test will be accepted for half credit until the next test.
\emph{Please remember that you will not be eligible to complete test corrections if you do not turn in your homework.}}

\section*{Equations}

\begin{align*}
  \Sigma \vec{F} &= m\vec{a} &
  w &= mg &
  f_s &\le \mu_s N &
  f_k &= \mu_k N
\end{align*}


\end{document}