\documentclass[10pt]{exam}
\usepackage[phy]{template-for-exam}
\usepackage{hyperref,enumitem}

\setlist[]{
    itemsep=-1ex,
  }

\title{Research Project - \\Workday \#1}
\author{Rohrbach}
\date{\today}

\begin{document}
\maketitle

\section*{General Project Reminders}

\begin{itemize}
  \item 
    You will be giving a 5-7 minute presentation the week before Spring Break on your topic.
  \item	
    Your project should be built around a diagram, graph, model, etc. that substantially contributes to our understanding of the topic.  A presentation aid (like PowerPoint, Prezi, etc.) is not a visual!
  \item
    In addition to your visual, you will likely want to have a presentation aid like a PowerPoint, a poster, or something similar.
  
\end{itemize}

\section*{What to do before we go to the library}

\subsection*{Step 1}
Start by writing down your topic from \texttt{\href{https://go.rohrbachscience.com/project-topics}{\bf https://go.rohrbachscience.com/project-topics}}.  Make sure to include any information in parentheses, as that information may help guide your research.

\begin{center}
  \fillin[][0.9\textwidth]
\end{center}

\subsection*{Step 2}

Please download and edit the template posted at \texttt{\href{https://go.rohrbachscience.com/bib-template}{\bf https://go.rohrbachscience.com/bib-template}}.

\subsection*{Step 3}

Open up Mrs. Kovach's Research Pathfinder at \texttt{\href{https://go.rohrbachscience.com/pathfinder}{\bf https://go.rohrbachscience.com/pathfinder}}.  There are excellent links to help you get started on your research.  

\section*{Your Assignment: An Annotated Bibliography}

Your goal for today is to find some good sources about your topic and to start learning about it.  The evidence that you've met the goal will be your Annotated Bibliography.

\vspace{1em}

\noindent
You need to find {\bf three sources} about your topic. Each source needs:
%
\begin{enumerate}
  \item An APA-style citation
  \item A paragraph explaining what you learned from that source
  \item One sentence evaluating the source.
  \item One sentence explaining how your source will help you explain your project topic.
\end{enumerate}
%
Please see the last few pages of the Research Pathfinder includes instructions on how to cite your three sources and complete their annotations.

\vspace{1em}

\noindent
Your Annotated Bibliography should be double spaced and have a hanging indent. It should be uploaded to Schoology by {\bf Wed, Feb 8 at 11:59pm}. 


\section*{Questions to Guide Your Research}

\emph{These are questions to help you if you get stuck.  I do not need you to turn in answers to these questions.}

\begin{enumerate}
  \item What will my visual be?  A diagram? A model? A graph? A flow chart?
  \item What is the science behind my topic?  Why is it interesting/important?
  \item (\emph{if you have a scientist}): What scientific theories is my person responsible for?
  \item (\emph{if you have a building project}): How will I build it?  What materials will I need?
\end{enumerate}

\section*{Project Timeline}

\begin{tabular}{ll}
  Wed, Feb 8 & 
  Annotated Bibliography due on Schoology by 11:59pm
  \\[1em]
  Tue-Thu, Feb 18-20 & 
  Library Research Day \#2 (Focus will be on preparing your presentation)
  \\[1em]
  Week of Mar 17-21 & 
  Presentations in class
  \\[1em]
  Sat, Mar 22 &
  Spring Break!
\end{tabular}

\end{document}