\documentclass[12pt]{exam}
\usepackage[phy]{template-for-exam}
\usepackage{tikz,ifthen,multicol,fdsymbol,my-tikz-clipart}
\footer{}{}{}
\header{}{}{}
\shadedsolutions
\printanswers

\newcommand{\h}{$\heartsuit$}
\renewcommand{\c}{$\clubsuit$}
\renewcommand{\d}{$\diamondsuit$}
\newcommand{\s}{$\spadesuit$}
\renewcommand{\ku}[3]{
  \ifprintanswers
    #1 #2 #3
  \else
    \begin{tabular}
      {p{.2\textwidth}|p{.2\textwidth}|p{.2\textwidth}}
      \small Knowns/Unknowns    &
      \small  Plug \& Chug      & 
      \small Answer w/ Units \\
      \center #1 &
      \center #2 &
      \center #3 \\[3em]
    \end{tabular}
  \fi
}


\begin{document}

%\Large

\def\mystrut{\protect\rule[-2.2ex]{0ex}{2.2ex}} 
\qformat{ \textbf{Task \#\thequestion}
  \ifthenelse{\equal{\thequestion}{\thequestiontitle}}
    {}
    {: \emph{\thequestiontitle}}
  \mystrut  \hfill}


\begin{questions}

\vspace*{\stretch{1}}

\question
  You apply a force of 549 N to push a refrigerator forward.  The friction acting on the refrigerator is 493 N.
  
  \begin{parts}
    \part Draw the Free-Body Diagram (\h)
    \part The mass of the refrigerator is 720 kg.  Calculate the acceleration. 

      \ku{\s}{\d}{\d}
  \end{parts}

  \begin{solution}
    $F_{NET}=56$ N; $0.078$ m/s$^2$
  \end{solution}


\vs \hrule \vs

\question

    A bucket in the a well is hoisted by a rope.  The mass of the bucket is 5.5 kg.

    \ifprintanswers
    \else
      \begin{tikzpicture}
        \path (0,-1.8) pic {bucket};
        \filldraw[pattern=north east lines] 
        (-.1,0) -- (.1,0) -- (.1,2) -- (-.1,2) -- cycle;
      \end{tikzpicture}
    \fi

    \begin{parts}
      \part Calculate the force of gravity acting on the bucket.
      
      \ku{\h}{\h}{\h}
  
      \part Draw a Free-Body Diagram of the bucket.  The tension on the rope is 71 N. (\s)
  
      \part Calculate the acceleration of the bucket
  
      \ku{\d}{\d}{\d}
  
  
    \end{parts}
  %

  \begin{solution}
    $F_G=53.9$ N; $F_{NET}=17.1$ N; $a=3.11$ m/s$^2$
  \end{solution}

\vs
\ifprintanswers
  \hrule \vs
\else
  \pagebreak
  \vspace*{\stretch{1}}

\fi

\question
  When the astronaut Neil Armstrong was fully suited up with all of his equipment, he had a weight (that is, force of gravity) on Earth of 1600 N.

  \begin{parts}
    \part Calculate Neil Armstrong's mass

    \ku{\s}{\s}{\s}

    \part When Neil Armstrong walked on the moon, the acceleration of gravity was only $g=1.61$~m/s$^2$.  Calculate Neil's force of gravity on the moon
    
    \ku{\d}{\d}{\d}

    \part Calculate Neil Armstrong's mass on the moon (\h)
  \end{parts}

  \begin{solution}
    $m=163.27$ kg; $F_{G_{moon}}=262.86$ N
  \end{solution}


\vs \hrule \vs

\question
  A certain elevator with mass 3200~kg is accelerating upward at a rate o 0.26~m/s$^2$.

  \begin{parts}
    \part Calculate the net force

    \ku{\s}{\s}{\s}

    \part Calculate the force of gravity
    
    \ku{\h}{\h}{\h}

    \part The elevator is being lifted by cables.  Draw the Free-Body Diagram. (\d)


    \part What must be the tension of the cables? (\d\h\s)

  \end{parts}

  \begin{solution}
    $F_{NET}=\SI{832}{\newton}$; $F_G=\SI{31360}{\newton}$; $F_T=\SI{32192}{\newton}$
  \end{solution}

\vs
\ifprintanswers
  \hrule \vs
\else
  \pagebreak
  \vspace*{\stretch{1}}

\fi

\question
  A loaded semi truck has a mass of \SI{36000}{\kilo\gram} It experiences \SI{16500}{\newton} of friction.  Its acceleration is \SI{0.12}{\meter\per\second^2}.

  \begin{parts}
    \part Calculate the net force acting on the truck.

    \ku{\d}{\s}{\s}

    \part Draw a Free-Body Diagram (\h)
    \part Calculate the force needed to be applied by the truck's engine. (\d\s\h)
  \end{parts}

  \begin{solution}
    $F_{NET}=\SI{4320}{\newton}$; $F_A=\SI{20820}{\newton}$
  \end{solution}


\vs \hrule \vs

\titledquestion{Challenge!}

  A 25-kg box is pushed forward with an acceleration of of 4.56~m/s$^2$. There are 152 N of friction.  Draw a Free-Body Diagram and label the magnitude of all four foces acting on the box.

  \begin{solution}
    $F_{NET}=114$ N; $F_A=266$ N; $F_f=152$ N; $F_N=242$ N; $F_G=242$ N;
  \end{solution}

\vs


\end{questions}




\end{document}