\documentclass[10pt]{exam}
\usepackage[icp]{template-for-exam}

\title{Measurement Lab \#1}
\author{Rohrbach}
\date{\today}

\begin{document}
\maketitle

\section{Graduated Cylinders}
\begin{enumerate}
  \item What quantity does the gradulated cylinder measure? \vs
  \item What are the units that the graduated cylinder measures in? \vs
  \item Measure the volume of the two liquids. {\bf Make sure to include units!}.
    \begin{enumerate}
      \item red liquid:\vs
      \item blue liquid:\vs
    \end{enumerate}
\end{enumerate}

\section{Thermometers}
\begin{enumerate}
  \item What quantity does the thermometer measure ? \vs
  \item What are the units that the balance measures in?  Do not use Ferenheit! \vs
  \item Measure the temperature of the air and the temperature of the water. {\bf Make sure to include units!}.
    \begin{enumerate}
      \item air:\vs
      \item water:\vs
    \end{enumerate}
\end{enumerate}


\section{Triple-Beam Balance}
\begin{enumerate}
  \item What quantity does the balance measure? \vs
  \item What are the units that the balance measures in? \vs
  \item Measure the mass of the wooden, metal, and plastic blocks.  {\bf Make sure to include units!}.
    \begin{enumerate}
      \item Wooden block: \vs
      \item Metal block: \vs
      \item Plastic block: \vs
    \end{enumerate}
\end{enumerate}

\pagebreak

\section{Ruler}
\begin{enumerate}
  \item What quantity does ruler measure? \vs
  \item What are the units that the ruler measures in?  Do not use inches! \vs
  \item Measure the height of the wooden, metal, and plastic cylinders.  {\bf Make sure to include units!}
    \begin{enumerate}
      \item Wooden cylinder: \vs
      \item Metal cylinder: \vs
      \item Plastic cylinder: \vs
    \end{enumerate}
\end{enumerate}

\section{Meter Stick}
\begin{enumerate}
  \item What quantity does the meter stick measure? \vs
  \item What are the units that the meter stick measures in?  Do not use inches! \vs
  \item Measure the length and width of the table (2 different measurements).  {\bf Make sure to include units!} \vs
  \item When would it be better to use a meter stick and when would it be better to use a ruler to make measurements? \vs[2]
\end{enumerate}


\section{Stopwatch}
\begin{enumerate}
  \item What quantity does the stopwatch measure? \vs
  \item What are the units that the stopwatch measures in? \vs
  \item Measure the time it takes for the stoplight to cycle from Red to Yellow to Green then back to Red.  (\emph{Start the timer when the red light turns on and then stop it the next time the red light turns on.})  {\bf Make sure your measurement includes units!} \vs
\end{enumerate}


\end{document}