\documentclass[10pt]{exam}
\usepackage[phy]{template-for-exam}
\usepackage{enumitem,boldline,multirow,makecell}
\setlist[enumerate]{topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex}
%\printanswers

\title{Stair Lab}
\author{Rohrbach}
\date{\today}

\begin{document}
\maketitle


\newcommand{\printeqs}{
  \begin{align*}
    W   &= F d          & 
    P   &= \frac{W}{t}  &
    F_G &= mg
  \end{align*}

  \vspace{-2em}
}

\vspace{-2em}
\printeqs
\vspace{-2em}

\ifprintanswers
  \vspace{3em}

  \begin{center}
    \color{red} 
    \hrule
    \Large \bf --- Makeup Assignment with Sample Data included. ---
    \hrule
  \end{center}

  \vspace{-2em}

\fi


\begin{questions}

\uplevel{\section*{Pre-Lab}}

\question
  \emph{Practice Problem:} A 20-kg box is lifted 3 m into the air:

  \begin{parts}
    \part 
      Calculate the force that you are doing work against.
      \vs[2]

    \part 
      How much work is needed to lift the box that high?
      \vs[2]
    
    \part
      If it took you 12 s to lift it 3 m, what is your power?
      \vs
  
  \end{parts}

  
  
  
  
  
\begin{EnvUplevel}

  \section*{Hypotheses}
  
  In this lab you will change the \emph{speed} you climb the stairs, the \emph{height} of the stairs, and the \emph{mass} you are carrying.

\end{EnvUplevel}

  
\question
  Which (if any) of these will affect work?  Explain why you think this.
  \vs[2]
  
  
\question
  Which (if any) of this will affect power?  Explain why you think this.
  \vs
  
  
\uplevel{\section*{Procedure}}
  \begin{enumerate}
    \item
      Pick two members of your group to go up the stairs.  Person A will carry 1 book; person B will carry 3 textbooks.
    \item
      Start at the bottom of the stairs for trial 1 (long stairs) or trial 2 (short stairs).
    \item
      One person in the group will time how long it takes person A to climb the stairs at a slow rate (think how fast you would go on a Monday morning).  Record the time
    \item 
      Return to the bottom of the stairs, and repeat step 
      \#2, but this time at a moderate pace (think how fast you go on a regular day)
    \item 
      Return to the bottom of the stairs, and repeat step \#2, but this time at a fast pace (think how fast you go if you're running late to class)
    \item 
      Repeat steps \#2-5, but this time do it for the other set of steps
    \item 
      Repeat steps \#2-6 with person B.
  \end{enumerate}

\pagebreak
\printeqs

\uplevel{\section*{Data}}

\renewcommand{\arraystretch}{2}
\newcommand{\samp}[1]{
  \ifprintanswers {\bf \color{red}#1 sec} \fi
}

\paragraph{Trial \#1: Tall stairs}\hfill

\begin{tabular}{|l|c|c|c|p{7em}|p{7em}|}
  \hline
  & Stair Height & Mass carried 
  & \centering\arraybackslash Climb Time (s)  
  & \centering\arraybackslash Work (J) 
  & \centering\arraybackslash Power (W) \\
  \hlineB{4}
  fast   & \multirow{6}{*}{3.5 m} & 
    \multirow{3}{*}{\shortstack{(1 book) \\ 2.7 kg}} 
                                    & \samp{1.8} & & \\
  \cline{1-1}\cline{4-6}
  medium & &                        & \samp{3.7} & & \\
  \cline{1-1}\cline{4-6}
  slow   & &                        & \samp{9.7} & & \\

  \clineB{1-1}{4}\clineB{3-6}{4}
  fast   & & 
    \multirow{3}{*}{\shortstack{(3 books) \\ 8.1 kg}} 
                                    & \samp{2.5} & & \\
  \cline{1-1}\cline{4-6}
  medium & &                        & \samp{4.4} & & \\
  \cline{1-1}\cline{4-6}
  slow   & &                        & \samp{10.6} & & \\
  \hlineB{4}
\end{tabular}

    
Show at least one calculation for work and at least one calculation for power:
\vs

\paragraph{Trial \#2: Short stairs}\hfill

\begin{tabular}{|l|c|c|c|p{7em}|p{7em}|}
  \hline
  & Stair Height & Mass carried 
  & \centering\arraybackslash Climb Time (s)  
  & \centering\arraybackslash Work (J) 
  & \centering\arraybackslash Power (W) \\
  \hlineB{4}
  fast   & \multirow{6}{*}{0.7 m} & 
    \multirow{3}{*}{\shortstack{(1 book) \\ 2.7 kg}} 
                                    & \samp{0.5} & & \\
  \cline{1-1}\cline{4-6}
  medium & &                        & \samp{0.8} & & \\
  \cline{1-1}\cline{4-6}
  slow   & &                        & \samp{2.2} & & \\

  \clineB{1-1}{4}\clineB{3-6}{4}
  fast   & & 
    \multirow{3}{*}{\shortstack{(3 books) \\ 8.1 kg}} 
                                    & \samp{0.6} & & \\
  \cline{1-1}\cline{4-6}
  medium & &                        & \samp{1.0} & & \\
  \cline{1-1}\cline{4-6}
  slow   & &                        & \samp{2.5} & & \\
  \hlineB{4}
\end{tabular}

    
Show at least one calculation for work and at least one calculation for power:
\vs

\pagebreak
\printeqs

\begin{EnvUplevel}

  \section*{Conclusion Questions}
  
  Justify all your answers using your data!!

\end{EnvUplevel}

\question
  Compare the work you did carrying one book vs. carrying multiple books.  How did mass seem to affect the amount of work done?
  \vs


\question
  Compare your power output for the different speeds in trial one.  How did the speed with which you climbed the stairs seem to affect your power?
  \vs

\question
  How did the height of the stairs seem to affect your work?
  \vs

\question
  Of the power calculations you made, which ones are similar?  Why does this make sense?
  \vs




\uplevel{\section*{Post-Lab}}

\question
  A crane lifts a 1200-kg car to height of 10 meters in a time of 8 seconds.  What power does the motor produce in accomplishing this task?
  \vs[2]

  

\end{questions}

\end{document}