\documentclass[10pt,landscape]{exam}
\usepackage[margin=0.5in]{geometry}
\usepackage{multicol}
\setlength{\columnsep}{1in}


\begin{document}


\begin{multicols*}{2}

\begin{questions}

\uplevel{\subsection*{Speed}}

  \question 
    What is the difference between instantaneous speed and average speed? \vfill

  \question
    If a car moves with an average speed of 60 km/h, how far will it travel in 4 hours? \vfill

  \question
    What is the average speed of a car that travels 40 km in one-half hour (0.5 hr)? \label{avg} \vfill

  \question
    Would the maximum speed of the car in \#\ref{avg} be larger than, smaller than, or equal to 80 km/h? \vfill

\uplevel{\subsection*{Velocity}}

  \question
    What is the difference between speed and velocity? \vfill

  \question
    The speedometer of a car moving east reads 100~km/h and the speedometer of a car moving west also reads 100~km/h.  Do they have the same speed?  Do they have the same velocity?
    \vfill

  \question
    During a certain period of time, the speedometer of a car reads a constant 60 km/h.  Does this indicate a constant speed?  Does it indicate a constant velocity?
    \vspace*{3em}

\columnbreak

\uplevel{\subsection*{Acceleration}}

  \question 
    What is acceleration? \vfill

  \question
    What is the acceleration of a car that goes from rest to 90 km/h in 10 seconds? \vfill

  \question
    What is the acceleration of a car that maintains a constant speed of 50 km/h for 10 seconds? \vfill

  \question
    There are three controls in a car that cause it to accelerate.  One of them is the accelerator.  What are the other two?
    \vspace*{7em}



\end{questions}

\end{multicols*}


\end{document}