\documentclass[12pt]{exam}
\usepackage[phy]{template-for-exam}
\usepackage{my-tikz-clipart}

\title{Motion \#1}
\author{Rohrbach}
\date{\today}

\begin{document}
\maketitle

\begin{questions}
  \question 
    Larry drives {\bf  25 km} east before he realizes he is going in the wrong direction.  He turns around and drives \SI{63000}{\meter} west.  Draw a picture, and calculate Larry's distance and displacement.
    \vs[2]

  \question
    Eunice has traveled 30 m through the hall when she realizes she dropped her phone in the hallway.  She turns around and walks 17 m back in the direction she came from.  She then turns back in her original direction, and walks 67 m to her next class.  Draw a picture, and calculate Eunice's distance and displacement.
    \vs[2]
  
  \question
    Draw a path where the distance and displacement are the same.  Sketch your path below and \emph{explain why they are the same.}
    \vs

  \question
    Draw a path where the displacement is zero but the distance is not.  Sketch your path below \emph{and explain.}
    \vs

  \pagebreak

  \question
    Why can you have a negative displacement, but not a negative distance?
    \vs

  \question
    Consider a car with a \emph{negative velocity} and \emph{positive acceleration}.

    \begin{parts}
      \part 
        Draw the velocity and acceleration vectors on this car.

        \begin{tikzpicture}
          \fill[pattern=north east lines] 
          (-8,0) rectangle (2,-.2);
          \path (-3,0.2) pic[scale=0.5] {car};
        \end{tikzpicture}

      \part
        Which direction is it traveling?  How do you know?
        \vs
      
      \part
        Is it speeding up or slowing down?  How do you know?
        \vs
    \end{parts}

  \question
    Consider a car with a \emph{positive velocity} and \emph{negative acceleration}.

    \begin{parts}
      \part 
        Draw the velocity and acceleration vectors on this car.

        \begin{tikzpicture}
          \fill[pattern=north east lines] 
          (-8,0) rectangle (2,-.2);
          \path (-3,0.2) pic[scale=0.5] {car};
        \end{tikzpicture}

      \part
        Which direction is it traveling?  How do you know?
        \vs
      
      \part
        Is it speeding up or slowing down?  How do you know?
        \vs
    \end{parts}
  
\end{questions}
\end{document}