\documentclass[10pt]{exam}
\usepackage[phy]{template-for-exam}
\usepackage{my-tikz-clipart}

\title{Motion \#2}
\author{Rohrbach}
\date{\today}

\begin{document}
\maketitle

\vspace{-2em}
\begin{questions}

  \begin{EnvUplevel}
    \paragraph{Velocity}
      Sara, an amazingly well-rounded athlete, participates in a grueling race.  Use the information to determine the answers to each question.
  \end{EnvUplevel}

  \question 
    Sara begins the race by running \SI{5000}{\meter} from the starting line to checkpoint 1 in \SI{1240}{\second}.  What is her velocity?
    \vs

  \question
    Next, Sara swims \SI{500}{\meter} from checkpoint 1 to checkpoint 2 with a velocity of \SI{1.1}{\meter\per\second}.  How long does it take her?
    \vs

  \question
    From checkpoint 2 she rides a bike with a velocity of \SI{4.9}{\meter\per\second} for \SI{3600}{\second}.  What is the displacement from checkpoint 2 to checkpoint 3?
    \vs 
  
  \question
    Sara must now run all the way back to the starting line to finish the race.  Completely exhausted, Sara decides to get launched by a large cannon that can blast her to the beginning.  What is her velocity to go from checkpoint 3 to the starting line if it takes her \SI{1157}{\second} to travel the displacement?
    \vs

  \pagebreak

  \question
    Calculate Sara's {\bf distance} for the entire race.  Also calculate her {\bf displacement}.
    \vs

  \question
    Calculate Sara's {\bf average speed} and {\bf average velocity}.
    \vs

    \begin{EnvUplevel}
      \hrule
      \paragraph{Acceleration}
        A brand new ride has opened at King's Island.  Use the information provided to answer the questions.
    \end{EnvUplevel}

  \question
    The ride starts at rest and then gets up to a speed of 50 m/s in 1.9 s.  What is its acceleration?
    \vs

  \question
    Once it is traveling at \SI{50}{\meter\per\second}, it accelerates at a rate of \SI{-9.2}{\meter\per\second^2} for \SI{3.0}{\second}.  What is its velocity after this time?
    \vs

  \question
    The ride now maintains a constant velocity for 10 s.  What is its acceleration during this time?
    \vs

  \question
    Finally, the ride comes to an abruot a stop in \SI{0.88}{\second}. What is its acceleration?
    \vs


 
\end{questions}
\end{document}